Designing Large-Scale Imaging Surveys for a Retrospective Relative Photometric Calibration

### 2012-08-24 paper/self_calibration_I.tex
minor text

\begin{figure}
\plotone{D_survey.pdf}
\figcaption{A summary of Survey Strategy D \surveyfigcaption. As can be seen in panel (c), this quasi-random survey offers a more uniform coverage of the field than the other survey investigated.
\label{fig:D_survey}}
\end{figure}

>>>>

\begin{figure}
\plotone{D_survey.pdf}
\figcaption{A summary of Survey Strategy D \surveyfigcaption. As can be seen in panel (c), this quasi-random survey offers a more uniform coverage of the field than the other surveys; it also has much more uniformity than would a Poisson distribution of field centers.
\label{fig:D_survey}}
\end{figure}
